Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-27 ms/main.tex
Add another sub figure to fig5

% Fluctuations in spatial model
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in a structured population.}
    The frequency of cooperators (green) and defectors (red) in a structured finite population.
    Both phenotypes start at 50\% frequency.
    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}

>>>>

% Fluctuations in spatial model
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.75]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf}~\\
   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in a structured population.}
    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
    Both phenotypes start at 50\% frequency.
    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
    }
    %TODO: revisit this caption.
    \label{fig:spatial_fluctuations}
  \end{figure}
